Weighted Model Counting with Conditional Measures

### 2020-07-28 paper/paper.tex
Move things around
Preliminary experimental results
Better plots
Describe experimental data

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{fullpage}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{hyperref}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage[capitalise]{cleveref}
\usepackage{bm}
\usepackage{booktabs}
\usepackage[table]{xcolor}
\usepackage{tikz}
\usepackage[backgroundcolor=lightgray]{todonotes}
\usepackage{complexity}
\usepackage{soul}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage[binary-units]{siunitx}

@@

\begin{itemize}
\item We don't compare 'compile times' because our encoding time is linear, so
  we would easily beat everyone else.
\item When the Bayesian network has an evidence file, we compute the probability
  of evidence. Otherwise, let $X$ denote the last-mentioned node in the Bayesian
  network. If $\mathsf{true}$ is a valid value of $X$, we compute the marginal
  probability of $X = \mathsf{true}$. Otherwise, we pick the first value of $X$
  and calculate its marginal probability. This applies to the Grid data set (as
  intended) and also to two instances of Plan Reconstruction and roughly half of
  the instances from 2004-PGM that have empty evidence files.
\item After the experiments are finished, note the processor, memory per thread.
\item The experiments were run on Intel Xeon Gold 6138 processor with an
  \SI{8}{\giga\byte} memory limit.
\item I will call my encoding \texttt{db20}.
\item All other encodings are implemented in
  Ace~3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} and were compiled
  with \texttt{-encodeOnly} (i.e., don't compile the CNF into an AC) and
  \texttt{-noEclause} (i.e., only use standard syntax) flags.
\item Datasets
  \begin{itemize}
  \item binary Bayesian networks from Sang et
    al.\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}
    \cite{DBLP:conf/aaai/SangBK05}
    \begin{itemize}
    \item Grid (networks) (ratio 75 means that 75\% of the nodes are
      deterministic),
    \item Plan recognition (problems),
    \item Deterministic quick medical reference (what do the numbers mean? the
      README doesn't say).
    \end{itemize}
  \item Bayesian networks available with Ace
    \begin{itemize}
    \item \texttt{2004-pgm} \cite{DBLP:journals/ijar/ChaviraDJ06} (binary)
    \item \texttt{2005-ijcai} \cite{DBLP:conf/ijcai/ChaviraD05}. The Genie/Smile
      files have their own citation data that I should probably extract. This is
      the only dataset that has some non-binary networks.
    \item \texttt{2006-ijar} \cite{DBLP:journals/ijar/ChaviraDJ06} (binary)
    \end{itemize}
  \end{itemize}
\item \texttt{cd05} relaxes the encoding so much that extra models become
  possible. They are supposed to be filtered out by the algorithm, but mine
  can't do that because it doesn't deal with models. Same for \texttt{cd06}
  because it's based on \texttt{cd05}.
\end{itemize}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{fullpage}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{hyperref}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage[capitalise]{cleveref}
\usepackage{bm}
\usepackage{booktabs}
\usepackage[table]{xcolor}
\usepackage{tikz}
\usepackage[backgroundcolor=lightgray]{todonotes}
\usepackage{complexity}
\usepackage{soul}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage[binary-units]{siunitx}
\usepackage[inline]{enumitem}

@@

\begin{figure}
  \centering
  \input{scatter.tex}
  \caption{Scatter plots}
\end{figure}

\begin{figure}
  \centering
  \input{cumulative.tex}
  \caption{Cumulative plot}
\end{figure}

\begin{table}
  \caption{Out of 1216 instances}
  \centering
  \begin{tabular}{lrrr}
    \toprule
    Encoding & Unique & Fastest & Solved \\
    \midrule
    \texttt{cd05} & 2 & 3 & 372 \\
    \texttt{cd06} & 0 & 1 & 351 \\
    \texttt{d02} & 41 & 99 & 726 \\
    \texttt{db20} & 228 & 871 & 901 \\
    \texttt{sbk05} & 6 & 36 & 687 \\
    \bottomrule
  \end{tabular}
\end{table}

\begin{itemize}
\item We don't compare 'compile times' because our encoding time is linear, so
  we would easily beat everyone else.
\item When the Bayesian network has an evidence file, we compute the probability
  of evidence. Otherwise, let $X$ denote the last-mentioned node in the Bayesian
  network. If $\mathsf{true}$ is a valid value of $X$, we compute the marginal
  probability of $X = \mathsf{true}$. Otherwise, we pick the first value of $X$
  and calculate its marginal probability. This applies to the Grid data set (as
  intended) and also to two instances of Plan Reconstruction and roughly half of
  the instances from 2004-PGM that have empty evidence files.
\item After the experiments are finished, note the processor, memory per thread.
\item The experiments were run on Intel Xeon Gold 6138 processor with an
  \SI{8}{\giga\byte} memory limit.
\item I will call my encoding \texttt{db20}.
\item All other encodings are implemented in
  Ace~3.0\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} and were compiled
  with \texttt{-encodeOnly} (i.e., don't compile the CNF into an AC) and
  \texttt{-noEclause} (i.e., only use standard syntax) flags.
\item We don't use Ace's evidence-encoding mechanism because it has multiple
  significant bugs (and the code is closed-source). Ace's implementation
  (depending on the exact encoding) is supposed to perform some simplifications
  when encoding evidence. We just do the trivial thing---no simplifications.
\item \texttt{cd05} relaxes the encoding so much that extra models become
  possible. They are supposed to be filtered out by the algorithm, but mine
  can't do that because it doesn't deal with models. Same for \texttt{cd06}
  because it's based on \texttt{cd05}.
\end{itemize}

\paragraph{Data.} For experiments, we use the Bayesian networks available
with Ace\footnote{\url{http://reasoning.cs.ucla.edu/ace/}} and
Cachet\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}, most of
which happen to be binary. We classify them into the following seven categories:
\begin{itemize*}
\item DQMR and
\item grid networks as described by Sang et al. \cite{DBLP:conf/aaai/SangBK05},
\item friends and smokers,
\item mastermind, and
\item random blocks from the work of Chavira et al.
  \cite{DBLP:journals/ijar/ChaviraDJ06},
\item remaining binary Bayesian networks that include plan recognition
  \cite{DBLP:conf/aaai/SangBK05}, students and professors
  \cite{DBLP:journals/ijar/ChaviraDJ06}, and \texttt{tcc4f}, and
\item non-binary classic Bayesian networks (\texttt{alarm}, \texttt{diabetes},
  \texttt{hailfinder}, \texttt{mildew}, \texttt{munin1}--\texttt{4},
  \texttt{pathfinder}, \texttt{pigs}, \texttt{water}).
\end{itemize*}
% DQMR
% Friends and smokers (2006)
% Grid
% Mastermind (2004 & some of 2005)
% Random blocks (2004 & some of 2005)
% Non-binary: most of 2005
% Other binary (whatever remains, including Plan Recognition)
